Data Management \\ and LSST Special Programs

### 2022-02-20 DMTN-065.tex
fix lse

For Special Programs which will require User-Generated pipelines and data products, note that users will have access to all of the LSST Science Pipelines and its data processing infrastructure, as well as dedicated computational resources next-to-the-data (via the Rubin Science Platform; \citeds{LSE-319}).
However, computationally intense processing might require external resources.

>>>>

For Special Programs which will require User-Generated pipelines and data products, note that users will have access to all of the LSST Science Pipelines and its data processing infrastructure, as well as dedicated computational resources next-to-the-data (via the Rubin Science Platform; \citeds{lse-319}).
Details of the planned ``User Batch" facility for data processing are described in \citeds{dmtn-202}.
However, very computationally intense processing might require external resources.
